Learning Augmented Joint-Space Task-Oriented Dynamical Systems: \\ A Linear Parameter Varying and Synergetic Control Approach

### 2017-11-17 paper/main_RA-L_v1_final.tex
8 pages paper!

\section{Discussion} 
\label{Sec:Dis}
In this paper, we have presented a dynamical system in joint space that is provably Lyapunov-stable in task space and which replicates demonstrated joint-space behaviors. The desired motions are fast to compute, and smoothly handle singularities by avoiding the pseudo-inverse Jacobian. We showed the system's ability to learn different joint-space behaviors on a redundant robotic platform.

One of the most important points when validating a learning from demonstration method is to evaluate the system's behavior away from demonstrations. When the current joint configuration is far from any of the local synergy regions, computing the scheduling parameters $\theta_k(\cdot)$ becomes numerically infeasible (all the Gaussians in \eqref{eq:A} $\rightarrow 0$), and so $\frac{1}{K}\sum\limits_{k=1}^{K}A_k$ is used to move the robot, which is still guaranteed to move towards the target. Moreover, in overlapping local regions where multiple $A_k$'s might be in conflict, the presented system compromises between them while still stably converging to the target. The reason for this is that rather than ``determining" the velocity of the system, our $\mathcal{A}$ matrix only warps it. This means that adding multiple ``conflicting" synergies amounts to nothing more than repeatedly warping the velocity, and still maintains the original stability property.

@@

Finally, as the proposed DS might get stuck at its kinematic joint limits, we are currently working on improving the performance of the proposed DS, by learning its parameters wrt. the kinematic constraints. In this way, we can ensure that the performance of the DS is kinematically feasible for the robot to  follow.

>>>>

\section{Discussion} 
\label{Sec:Dis}
In this paper, we have presented a dynamical system in joint space that is provably asymptotically stable in task space to a fixed target while replicating demonstrated joint-space behaviors. The desired motions are fast to compute, and smoothly handle singularities by avoiding the pseudo-inverse Jacobian.  We showed the system's ability to learn different joint-space behaviors on a robotic platform.

One of the most important points when validating a learning from demonstration method is to evaluate the system's behavior away from demonstrations.
 When the current joint configuration is far from any of the local synergy regions, computing the scheduling parameters $\theta_k(\cdot)$ becomes numerically infeasible (all the Gaussians in \eqref{eq:A} $\rightarrow 0$), and so $\frac{1}{K}\sum\limits_{k=1}^{K}A_k$ is used to move the robot, which is still guaranteed to move towards the target. %Moreover, in overlapping local regions where multiple $A_k$'s might be in conflict, the presented system compromises between them while still stably converging to the target. The reason for this is that rather than ``determining" the velocity of the system, our $\mathcal{A}$ matrix only warps it. This means that adding multiple ``conflicting" synergies amounts to nothing more than repeatedly warping the velocity, and still maintains the original stability property.

@@

Finally,  we are currently working on improving the performance of the proposed DS, by learning its parameters wrt. the kinematic constraints. In this way, we can ensure that the performance of the DS is kinematically feasible for the robot to  follow.
